\documentclass[10pt]{article}
\usepackage[a4paper, left=0.40in, right=0.40in, top=0.25in, bottom=0.15in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{resume}


\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{2}
    \raggedright
    \textbf{\LARGE Rejaul Islam}\\
    \normalsize{\textbf{PhD Candidate, Auburn University}}\\[1ex]
    \columnbreak
    \raggedleft
    \textbf{Address:} Auburn, AL 36830\\
    \textbf{Phone:} (334) 524-9464\\
    \textbf{Email:} \href{mailto:rzi0007@auburn.edu}{rzi0007@auburn.edu}\\
    \textbf{LinkedIn:} \href{http://www.linkedin.com/in/rejaul}{www.linkedin.com/in/rejaul}
\end{multicols}

\spacedhrule{-1.0ex}{-0.5ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\roottitle{SUMMARY}
\vspace{-1.0ex}
\begin{circlist}
    \item Interdisciplinary scientist with skills and experience in Biochemistry, Molecular Biology, and Computational Chemistry
    \item Possesses extensive expertise in enzyme kinetics and mechanisms
    \item Self-motivated, problem-solving and collaborative scientist with excellent communication skills
    \item Led collaborative projects, resulting in 7 publications and presentations, including 3 first-authored publications
    \item Seeking to contribute expertise across various biochemical facets, catalyzing advancements in Drug Discovery.
\end{circlist}

\spacedhrule{0.8ex}{0.0ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\roottitle{SKILLS}

\textbf{\textit{Technical Skills}}

\begin{indentsection}
	\skill{Protein Biochemistry}{Protein Expression, Purification, Characterization, Enzyme Kinetics, Inhibition Assays}
	\skill{Chromatography \& Mass Spectrometry}{AKTA FPLC, GC-MS, HPLC, LC-MS, ESI-MS, IEC, SEC, AC}
	\skill{Spectroscopy}{UV-Vis, Fluorescence, IR, Circular Dichroism}
	\skill{Electrophoresis}{Agarose, PAGE, CE, Native, IEF}
	\skill{Molecular Biology}{PCR, Cloning, Site-Directed Mutagenesis, Western blot, ELISA, Recombinant DNA Technology}
    \skill{Industrial Pharmacy}{cGLP, cGMP, SOP, QIR, Formulation, Validation, Development}\\
    \\
    \textbf{\textit{Software Proficiency}}
	\skill{Data Analysis}{Prism, Origin, KinTek Explorer, SnapGene, R, STATA}
    \skill{Proteomics \& Bioinformatics}{BLAST, ClustalW, Galaxy}
    \skill{Computational Chemistry}{AMBER, AutoDock, DOCK, PyMOL, Chimera, VM}
\end{indentsection}

\spacedhrule{0.8ex}{0.0ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\roottitle{EDUCATION}

\headedsubsection
{{{PhD candidate in Biochemistry,}} {\href{https://www.auburn.edu/}{\textbf{Auburn University},} {Auburn, Alabama}}}
{\period{Sep}{2017}{Jun}{2024 (expected)}}
{\vspace{-2.4ex}
}
\headedsubsection
{{MA in International Development,} {\href{https://www.iuj.ac.jp/}{\textbf{International University of Japan},} {Niigata, Japan}}}
{\period{Sep}{2012}{Jun}{2014}}
{\vspace{-2.4ex}
}
\headedsubsection
{{MS in Biochemistry and Molecular Biology,} {\href{https://juniv.edu/}{\textbf{Jahangirnagar University},} {Dhaka, Bangladesh}}}
{\period{Jun}{2010}{Nov}{2011}}
{\vspace{-2.4ex}
}

\spacedhrule{0.8ex}{0.0ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\roottitle{WORK EXPERIENCE}

\headedsection
{\href{https://www.ynu.ac.jp/english/}{Yokohama National University}}
{Yokohama, Japan}
{Industry-Academia-Government Collaboration Researcher}
{\period{Jan}{2015}{Mar}{2016}}
{\vspace{-2.4ex}
	\begin{circlist}
	\item Computed and assessed the ecosystem services provided by Blue Carbon (Japanese mangroves as well as global) to steer policymakers toward informed decision-making and strategic direction.	
    \item Conducted research on renewable energy, climate change mitigation \& adaptation, and avian collisions, aiming for comprehensive analysis and strategic insights.
	\end{circlist}
}

\headedsection
{\href{https://www.squarepharma.com.bd/}{Square Pharmaceuticals PLC.}}
{Dhaka, Bangladesh}
{Quality Assurance/Control Executive}
{\period{Sep}{2011}{Sep}{2012}}{
\vspace{-2.4ex}
\begin{circlist}	
    \item Coordinated the preparation and governance of standard operating procedures (SOPs), ensuring meticulous control over QMS-related documentation for six highly sought-after pharmaceutical products.
    \item Managed Market Compliance, Deviation, QIR (Quality Incident Report), CAPA (Corrective and Preventive Actions), NCR (Non-Conformance Report), and resolutions for rejections.
    \item Orchestrated and conducted analytical evaluations for raw materials, packaging materials, and finished products.
    \item Developed specifications, test procedures, and comprehensive analytical test reports for bulk products.
\end{circlist}
}

\spacedhrule{0.8ex}{0.0ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\roottitle{RESEARCH EXPERIENCE}

\headedsection
{\href{https://www.auburn.edu/}{Auburn University}}
{Auburn, Alabama}
{{PhD Thesis Research.} Guide: {\href{https://webhome.auburn.edu/~goodwdc/}{Dr. Doug Goodwin}}}
{\period{Sep}{2017}{Jun}{2024 (expected)}}
{\vspace{-2.4ex}
	\begin{circlist}
        \item Created and assembled vectors, followed by the subsequent steps of expressing, purifying, assaying, and analyzing the kinetics of the \textit{Mycobacterium tuberculosis} shikimate dehydrogenase (\textit{Mt}SDH).
        \item Engineered 3 Tryptophan variants of \textit{Mycobacterium tuberculosis} shikimate kinase (\textit{Mt}SK) to target pivotal positions for mechanistic exploration, employing Intrinsic Protein Fluorescence. 
        \item Innovating novel multi-target inhibitors targeting critical shikimate pathway enzymes, \textit{i.e.} \textit{Mt}SK and \textit{Mt}SDH, employing a fusion of experimental and computational tools to combat antibiotic resistant tuberculosis.
	\end{circlist}
}

\headedsection
{\href{https://www.iuj.ac.jp/}{International University of Japan}}
{Niigata, Japan}
{{MA Thesis Research.} Guide: {\href{https://www.kochi-tech.ac.jp/profile/en/kotani-koji.html/}{Dr. Koji Kotani}}}
{\period{Sep}{2012}{Jun}{2014}}
{\vspace{-2.4ex}
	\begin{circlist}
		\item Assessed the influence of farmers' climate change perception on adaptation strategies, pinpointing 3 key driving factors.
	\end{circlist}
}

\headedsection
{\href{https://juniv.edu/}{Jahangirnagar University}}
{Dhaka, Bangladesh}
{{MS Thesis Research.} Guide: {\href{https://www.juniv.edu/teachers/nazibur}{Dr. Md. Nazibur Rahman}}}
{\period{Jun}{2010}{Nov}{2011}}
{\vspace{-2.4ex}
	\begin{circlist}
		\item Evaluated fatty acid composition via GC-MS for four key nontraditional oil seeds in Bangladesh, detailing their health benefits
	\end{circlist}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\begin{multicols}{2}
    \raggedright
    \normalsize{Rejaul Islam}\\[1ex]
    \columnbreak
    \raggedleft Page 2\\
\end{multicols}
\spacedhrule{-1.0ex}{-0.5ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\roottitle{ACADEMIC EXPERIENCE}

\headedsectionthree
{Graduate Research \& Teaching Assistant}{\period{Sep}{2017}{Dec}{2023}}
{\href{https://www.auburn.edu/}{Auburn University,} {Auburn, Alabama}}
{\vspace{-2.4ex}
    \begin{circlist}
        \item Instructing approximately 50 students per semester in Advanced Biochemistry techniques. 
        \item Taught Organic Chemistry Laboratory I \& II as well as General Chemistry Laboratory I \& II to over 700 students.
        \item Mentored 1 graduate and 3 undergraduate students in their day-to-day lab activities.
    \end{circlist}
}

\spacedhrule{0.8ex}{0.0ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\roottitle{CONFERENCE PRESENTATIONS}
\begin{enumerate}
    \item Mazumder, M. M. R., \textbf{Islam, R}., \& Islam, R. (2023). Dithiolate-Based Scorpion Arm Ligand Synthesis and Characterization. \href{https://ecs.confex.com/ecs/244/meetingapp.cgi/Paper/181554}{\textit{In Proceedings of the 244th ECS Meeting}} (pp. XX-XX). Gothenburg, Sweden.
    \item \textbf{Islam, R}., \& Goodwin, D. C. (2023). Shikimate Pathway Enzymes as Candidates for Multitarget Inhibitor Development. \href{https://sec.gsu.edu/files/2023/04/13th-SEC-Program-Booklet-Final.pdf}{\textit{In 13th Southeast Enzyme Conference}} (pp. 01-27). Atlanta, GA.
    \item \textbf{Islam, R}., \& Matsuda, H. (2016). Valuation of Ecosystem Services Provided by “Blue Carbon.” \href{https://www.esj.ne.jp/meeting/abst/63/P2-391.html}{\textit{In The 63rd Annual Conference of The Ecological Society of Japan}}  (p. 391). Sendai, Japan.
\end{enumerate}

\spacedhrule{0.8ex}{0.0ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\roottitle{PUBLICATIONS}

\begin{enumerate}
    \item \textbf{Islam, R}., Islam, M., \& Managi, S. (In Press). Relationship of trade openness and renewable energy with nitrogen intensity in ecosystems. \href{https://link.springer.com/journal/11625}{\textit{Sustainability Science}.}
    \item Barton, C., Gasaway, K. C., \textbf{Islam, R}., Aziz, T., Krewall, J., Punthrangkul, D., \& Willian, K. R. (2022). Implementation of an At-Home, First-Semester Biochemistry Lab Course: A Module Based on Banana Tyrosinase. \textit{Journal of Chemical Education}, 99(4), 1571-1578. \href{https://doi.org/10.1021/acs.jchemed.1c00675}{doi:10.1021/acs.jchemed.1c00675}
    \item \textbf{Islam, R}., Rahman, S., Hasan, M. M., Akter, S., Hasan, M. A., Parvin, A., . . . Rahman, M. (2015). Analysis of fatty acid composition of four well known non-edible seeds in Bangladesh. \href{https://www.researchgate.net/publication/303100510_Analysis_of_fatty_acid_composition_of_four_well_known_non-edible_seeds_in_Bangladesh}{\textit{Jahangirnagar University Environmental Bulletin,}} 4, 1-9.
    \item \textbf{Islam, R}. (2014). Agricultural adaptation for food security: A case study from Bangladesh. \textit{International University of Japan}.
\end{enumerate}

\spacedhrule{0.8ex}{0.0ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}